\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\

### 2019-03-25 paper.tex
version 0.2.1 add motivation

\subsection{Our Motivation}

\section{Approximate Code}
\subsection{Design of Approximate Code}
\subsection{Encoding and Decoding Processes}
\subsection{Proof of Correctness}
\subsection{Properties of Approximate Code}

>>>>

\subsection{Our Motivation}
Based on Table 1, the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons. First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks. However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large. Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust. To solve these two problems, we propose a new erasure code called approximation code. It provides different fault tolerance between important and non-critical data to reduce storage overhead and protect critical data better.

\section{Approximate Code}

\subsection{Design of Approximate Code}
\subsection{Encoding and Decoding Processes}
\subsection{Proof of Correctness}
\subsection{Properties of Approximate Code}
